Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-02-02 ITiCSE2019.tex
Added policy link and updated submitted FIE abstract

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). Whilst various national and international model curricula and recommendations have been presented and discussed in recent years, in this paper we attempt to address the questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called “information assurance” in the UK and Europe, which worked, even if not well, in a sequential process model.

In the world of software and systems development, we have seen the disruption of Agile (invented c.2001) and DevOps (invented c.2009), but not necessarily through the lens of security; however, more recently there has been a recognition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. Thus, in the context of widespread international computer science/engineering curriculum reform – both in compulsory, as well as post-compulsory education – what does this trend mean more generally for institutions and educators, and how do we teach it?

In this paper, we frame a key social, cultural and economic global challenge in computing and engineering education by analysing the UK perspective on cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future cybersecurity educational initiatives, including practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions. 
\end{abstract}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some Cybersecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
There are various levels of specialism at which Cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general CS graduate.
\begin{description}
\item[RQ1]What should be taught to the generalist, and how?
\item[RQ2]Should this be taught stand-alone or integrated? 
\item[RQ3]How might accreditation regard Cybersecurity Education, or help with it?
\end{description}
\cite[p.~97]{ACM2013a} takes a distinct view on RQ2:
\begin{quote}
The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other Knowledge Areas.
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other Knowledge Areas.
%\pagebreak - to fix URL issues
\section{Policy Context}

>>>>

\begin{abstract}
% submitted abstract (100-500 word limit):
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, to social and technical (as well as other important dimensions). A multitude of national and international model curricula and recommendations - from national academies, learned societies and even governments -- have been presented and discussed in recent years, with varying levels of impact on policy and practice. In this paper we attempt to address the key questions ``what should the generalist computer scientist/engineer know'' and ``how well is that being taught''. (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters-level discipline; or left for development in professional practice, sometimes called ``information assurance'' in the UK and Europe, which worked, even if not well, in a sequential process model.

For example, in the world of software and systems development, we have seen the disruption of Agile (invented c.2001) and DevOps (invented c.2009), but not necessarily through the lens of security; however, more recently there has been a recognition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. Thus, in the context of widespread international computer science/engineering curriculum reform - both in compulsory, as well as post-compulsory education - what does this trend mean more generally for institutions and educators, and how do we teach it?

In this paper, we frame a key social, cultural and economic global challenge of cybersecurity in computing and engineering education by analysing the UK's national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities (and into industry and professional practice). Through this analysis of UK educational policy and practice, we make a number of recommendations for future cybersecurity educational initiatives and interventions, including a number of innovative practical suggestions for educators and curriculum designers, with a view for potential adoption and adaption in other jurisdictions internationally.
\end{abstract}

@@

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some Cybersecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
There are various levels of specialism at which Cybersecurity education can be addressed.
\begin{enumerate}
\item The person in the street --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
The focus of this paper is on 2--3: the general CS graduate.
\begin{description}
\item[RQ1]What should be taught to the generalist, and how?
\item[RQ2]Should this be taught stand-alone or integrated? 
\item[RQ3]How might accreditation regard Cybersecurity Education, or help with it?
\end{description}
\cite[p.~97]{ACM2013a} takes a distinct view on RQ2:
\begin{quote}
The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other Knowledge Areas.
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other Knowledge Areas.
%\pagebreak - to fix URL issues

\section{Policy Context}

% TC to add policy+skills context
% inc. new EU Cybersecurity Act: https://ec.europa.eu/commission/news/cybersecurity-act-2018-dec-11_en
